
\addcontentsline{toc}{section}{Список литературы}
\begin{thebibliography}{00}
	
\bibitem{das:survey} 
\textit{Soumendu Das et al.} Survey of Pattern Recognition Approaches in Japanese Character Recognition //\\
(IJCSIT) International Journal of Computer Science and Information Technologies, Vol. 5(1), 2014. P.~93--99.

\bibitem{nagata:shape} 
\textit{Nagata, Masaaki} Japanese OCR Error Correction using Character Shape Similarity and Statistical Language Model //\\
Proceedings of the 17th International Conference on Computational Linguistics - Volume 2, 1998. P.~922--928.

\bibitem{nagata:context} 
\textit{Nagata, Masaaki} Context-based Spelling Correction for Japanese OCR //\\
Proceedings of the 16th Conference on Computational Linguistics - Volume 2, 1996. P.~806--811.

\bibitem{katz:backoff} 
\textit{S. Katz} Estimation of probabilities from sparse data for the language model component of a speech recognizer. //\\
IEEE Transactions on Acoustics, Speech, and Signal Processing, vol. 35, no. 3, 1987. P.~400--401.

\bibitem{python:pygtrie} Pygtrie documentation [Электронный ресурс]. \\ URL: http://pygtrie.readthedocs.io/en/latest/ -- 2014

\bibitem{python:pygtrierepo} Pygtrie github [Электронный ресурс]. \\ URL: https://github.com/google/pygtrie -- 2017

\bibitem{python:nltk} Natural Language Toolkit [Электронный ресурс]. \\ URL: http://www.nltk.org/ -- 2017

\bibitem{python:dammit} Beautiful Soup Documentation [Электронный ресурс]. \\ URL: https://www.crummy.com/software/BeautifulSoup/bs4/doc/ -- 2015

\bibitem{tsai:dcnn} 
\textit{Tsai, Charlie} Recognizing Handwritten Japanese Characters Using Deep Convolutional Neural Networks //\\
URL: http://cs231n.stanford.edu/reports/2016/pdfs/262\_Report.

\bibitem{JISX0208}
Update Registration 87 Japanese Graphic Character Set for Information Interchange [Электронный ресурс]. \\
URL: https://web.archive.org/web/20150318013247/\\http://kikaku.itscj.ipsj.or.jp/ISO-IR/168.pdf -- 1992

\bibitem{manning}
\textit{Christopher D. Manning, Hinrich Schütze} Foundations of Statistical Natural Language Processing //
MIT Press, 1999.

\bibitem{corpus:edr} EDR Japanese Corpus Version 1.0 [Электронный ресурс]. \\ URL: http://www2.nict.go.jp/ipp/EDR/ENG/E\_Struct/E\_Struct-CPS.html -- 1991

\bibitem{corpus:atr} ATR Dialogue Database [Электронный ресурс]. \\ URL: http://shachi.org/resources/3450 -- 1990

\bibitem{chung:bunsetsu}
\textit{Sungyup Chung and Keikichi Hirose and Nobuaki Minematsu} N-gram language modeling of Japanese using bunsetsu boundaries //\\
INTERSPEECH, 2004.

\bibitem{kudo:crfs} 
\textit{Kudo, Taku and Yamamoto, Kaoru and Matsumoto, Yuji} Applying Conditional Random Fields to Japanese Morphological Analysis //\\
Proceedings of EMNLP 2004, 2004. P.~230--237.

\todo{дописать библиографию}

\end{thebibliography}